Checkpoint 4

### 2020-05-03 Draft-Report.Rmd
changes

For our first model we decided to use a simple Normal regression model.

@@

$$\begin{aligned}
Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
\sigma,\sigma \sim Exp(...)\\
\end{aligned}$$

@@

*White, StateColor, Day, Positive Cases, State

$$
Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_3X_3,\sigma_w^2) \\
\theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
\mu \sim N(..., ...) \\ 
\beta_2 \sim N(..., ...) \\
\beta_3 \sim N(..., ...) \\
\beta_4 \sim N(..., ...) \\
\sigma_w \sim Exp(...)\\
\sigma_b \sim Exp(...)\\
$$

@@

Variables of Interest: `White`, `StateColor`, `Day`, `Total Test Results`, `State`

@@

$$
\begin{split}
Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0 & \sim N(..., ...) \\
\beta_1 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$

>>>>

For our first model we decided to use a simple Repeated Measures regression model

$$\begin{aligned}
Y_{ij}|\theta, \mu, \sigma_w, \sigma_b \sim N(\theta_i,\theta_w^2)\\
\theta|\mu,\sigma_b \overset{ind}{\sim} N(\mu, \sigma_b^2)\\
\sigma_b,\sigma_w \sim Exp(...)
\end{aligned}$$

```{r}
set.seed(454)
model_0 <- stan_glmer(
  ChinaVirusInterest ~ (1 | State),
  data = model_data, family = gaussian,
)
```

For this model we decided to use a simple Normal regression model.

@@

$$\begin{aligned}
i = state, j = \text{days since "2020-03-14"} \\
Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4,\sigma^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
\sigma \sim Exp(...)\\
\end{aligned}$$

@@

*White, StateColor, Day, Positive Cases, State
$$\begin{aligned}
i = state, j = \text{days since "2020-03-14"}
Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b \sim N(\theta_i +\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
\theta_i|\mu, \sigma_b \overset{ind}{\sim}N (\mu, \sigma_b^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
\sigma_w,\sigma_b \sim Exp(...)\\
\end{aligned}$$

@@

Variables of Interest: `percent_white`, `StateColor`, `Day`, `Total Test Results`, `State`

@@

$$
\begin{split}
Y = \text{ChinaVirusInterest},i = state, j = \text{days since "2020-03-14"}, X_{ij} = \text{Days}\\
X_2 = \text{percent_white},,X_3 =\text{StateColor},  X_4 =\text{Total Test Results} \\
Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0,\beta_1,\beta_2,\beta_3,\beta_4 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$
